Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2016-05-06 tese2/11_related_work_collaboration.tex
[RFT] state of art nearly closed

	{\color{blue}\emph{Etherpad Lite} is a collaborative text editor implemented with \emph{NodeJS} that allows not only the basic text operations but also to associate authorships to pieces of text. It supports adding functionality through plug-ins\footnote{\url{http://static.etherpad.org/plugins.html}(Accessed 20 March 2016)}, for example:
		\begin{itemize}
		\item exporting and importing document formats such as \emph{DOC}, \emph{PDF}, \emph{ODT} and \emph{DOCX}.
		\item painting and drawing.
		\item video and audio chat using WebRTC.
		\item create sideshows.
		\item spell checking.
		\item text to speech.
		\end{itemize}
	}
%RP acho que não vale a pena fazer o itemize. Podia ficar tudo na linha, assim: 1, 2, 3...

>>>>

	{\color{blue}\emph{Etherpad Lite} is a collaborative text editor implemented with \emph{NodeJS} that allows not only the basic text operations but also to associate authorships to pieces of text. It supports adding functionality through plug-ins\footnote{\url{http://static.etherpad.org/plugins.html}(Accessed 20 March 2016)}, for example: exporting and importing document formats such as \emph{DOC}, \emph{PDF}, \emph{ODT} and \emph{DOCX}, painting and drawing, video and audio chat using WebRTC, create sideshows, spell checking and text to speech.
	}
%RP acho que não vale a pena fazer o itemize. Podia ficar tudo na linha, assim: 1, 2, 3...
